% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, top=0.6in, left=0.4in, right=0.4in, bottom=0.4in}
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage[hidelinks]{hyperref} % For hyperlinks
\usepackage{textcomp}
\hyphenpenalty=10000
\exhyphenpenalty=10000

% Formatting
\setlist{noitemsep, topsep=4pt, partopsep=4pt} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large DIVJOT SINGH MANCHANDA}\\[3pt]
\textit{AI Engineer | Builder of Agentic Systems | FinTech \& Cognitive AI Researcher}\\[2pt]
Mumbai, India | \href{mailto:djsmanchanda@gmail.com}{djsmanchanda@gmail.com} | +91 9137488435 | \href{https://www.linkedin.com/in/djsmanchanda}{linkedin.com/in/djsmanchanda} |  \href{https://github.com/djsmanchanda}{github.com/djsmanchanda} % Contact info
\end{center}

% Experience Section
\section*{EXPERIENCE}
\noindent
\textbf{IIT Madras, CAMS IIT-M Fintech Innovation Lab} \hfill Chennai, Tamil Nadu\\ % Company name and location
\textit{Research Intern} \hfill June 2024 – August 2024 % Position and duration
\begin{itemize}
    \item Performed feasibility analysis to explore the integration of AI in financial modeling and fintech solutions.
    \item Fine-tuned a RAG-based LLM on financial data with web search capabilities.
\end{itemize}

\noindent
\textbf{Renault Nissan} \hfill Chennai, Tamil Nadu\\ % Company name and location
\textit{Technical Intern} \hfill September 2024 – November 2024 % Position and duration
\begin{itemize}
    \item Developed an algorithm to evaluate past part vendors based on pricing, lead time, MOQ, quality, defect rates and other variables, enabling data-driven reordering decisions and \textbf{reducing decision-making time by 60\%}.
    \item Designed a chatbot to simplify access to the vendor analysis data using structured outputs, improving decision-making efficiency.
\end{itemize}

\noindent
\textbf{FlowNow} \hfill Berkeley, California\\ % Company name and location
\textit{Technical Intern} \hfill March 2025 – June 2025 % Position and duration
\begin{itemize}
    \item Built an \textbf{agentic AI system} creating context-aware questions from user-submitted books to assess their reading comprehension.
    \item Built an AI model to track user attention span using behavioral metrics, providing real-time insights and measuring the effectiveness of FlowNow's \textbf{neuroscience-based}, gamified training system.
    \item Integrated a \textbf{Tawk.to}-powered automated support agent to enhance onboarding and improve user engagement.
\end{itemize}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{SRM Institute of Science and Technology}, Kattankulathur, Tamil Nadu \hfill Enrolled: September 2022 | Expected: June 2026\\ % University name and location
Bachelor of Technology in \textbf{Artificial Intelligence} \hfill \textbf{CGPA: 8.54/10}\\[0.15em]
Relevant Coursework: Neural Networks and Machine Learning, Deep Learning Techniques, Design in Artificial Intelligence Products, Inferential Statistics and Predictive Analytics, Advanced Calculus, Image and Video Processing, Reinforcement Learning.

\vspace{0.5em}\noindent
\textbf{University of California, Berkeley}, Berkeley, California \hfill January 2025 – May 2025\\
\textit{Semester Abroad Program – SCET Startup Semester} \hfill \textbf{GPA: 4.0/4.0}\\[0.15em]
Courses: Deep Learning for Visual Data, Future of Technology \textit{(Designing Next-Generation Technologies)}, Amazoogle \textit{(AI and the Modern Data-Driven Business Model)}, Challenge Lab \textit{(Designing Startups to Transform Society)}, A. Richard Newton Lecture Series.

% Projects Section
\section*{PROJECTS}

\noindent
\textbf{Youtrition} \hfill UC Berkeley, California\\
\textit{Project Link:} \url{https://github.com/djsmanchanda/Youtrition} \hfill March 2025 – May 2025
\begin{itemize}
    \item Developed a personalized AI nutrition assistant analyzing users’ diet patterns and fridge contents to recommend balanced meals.
    \item Integrated the Gemini API for visual food recognition and structured parsing to classify items as fresh, spoiled, or old.
    \item Designed an intuitive Next.js dashboard with automated image-based inventory updates and adaptive nutritional insights.
    \item Created as part of the SCET Startup Semester at UC Berkeley, it combines AI, entrepreneurship, and product design.
\end{itemize}

\vspace{0.2em}

\noindent
\textbf{Reflection} (Llama Stack Hackathon) \hfill Berkeley, California\\
\textit{Project Link:} \url{https://github.com/djsmanchanda/Reflection} \hfill May 2025 – June 2025
\begin{itemize}
    \item Built an agentic AI assistant parsing emails, calendars, and chats to autonomously manage tasks and communication.
    \item Integrated Qdrant with Gemini embeddings to store contextual memory and support adaptive reasoning.
    \item Learned user priorities and typing style from past emails to personalize scheduling and email drafting.
    \item Generated email drafts that users can edit or reprompt before sending, ensuring control and accuracy in communication.
\end{itemize}

\vspace{0.2em}

\noindent
\textbf{Vogue Fusion} (PULSE Hackathon) \hfill IIT Bombay\\
\textit{Project Link:} \url{https://github.com/djsmanchanda/VogueFusion_Pulse} \hfill November 2024 – December 2024
\begin{itemize}
    \item Secured \textbf{2nd place} out of 500 teams at the PULSE Hackathon, IIT Bombay, winning INR 1L in prize money.
    \item Developed an algorithm using the Pinscrape API for seasonal trend analysis in fast-fashion lines for the Aditya Birla Group.
    \item Built ComfyUI workflows leveraging SDXL and custom LoRAs to automate design processes and reduce time-to-market.
    \item Designed a custom genetic algorithm to generate reproducible dye mixtures and predict printing costs within \textbf{7\% MOE}.
\end{itemize}

\vspace{0.2em}

\noindent
\textbf{MirrorBot} \hfill Intel Unnati AI Labs\\
\textit{Project Link:} \url{https://github.com/djsmanchanda/MirrorBot} \hfill August 2024 – December 2024
\begin{itemize}
    \item Implemented data preprocessing of users' past Instagram and WhatsApp chat histories to ensure relevant content extraction.
    \item Fine-tuned LLaMA 3.2 (3B) on the curated dataset to replicate the creator's messaging style and natural conversational flow.
    \item Conducted as part of the \href{https://drive.google.com/file/d/19qXnH3R2kTSqghv5wdkE-2p2tb6FoV1I}{Intel Unnati Generative AI Industrial Training – 2024}.
\end{itemize}

% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, C, C++, CUDA, PowerShell, Bash
    \item \textbf{Frameworks \& Libraries:} PyTorch, TensorFlow, Keras, Hugging Face, LangChain, Flask, Streamlit, React, Next.js, ComfyUI
    \item \textbf{Tools and Platforms:} Git, Weights and Biases, Docker, AWS EC2, AWS S3, AWS Lambda
\end{itemize}

% Achievements
\section*{ACHIEVEMENTS}
Won 6 hackathons and competitions with cumulative cash prizes exceeding \textbf{INR 2,00,000 and USD 1,000}.
\begin{itemize}
    \item \textbf{1st place} – HackStreet 2.0, SRM, Chennai \hfill March 2024
    \item \textbf{2nd place} – Llama Stack Challenge, UC Berkeley, California \hfill April 2025
    \item \textbf{2nd place} – PULSE Hackathon, Techfest IIT Bombay \hfill December 2024    
    \item \textbf{2nd place} – Innofusion'24, SRM, Chennai \hfill February 2024
    \item \textbf{3rd place} – Google Cloud Hacknight, San Francisco \hfill May 2025
    \item \textbf{3rd place} – Synapses 2.0, National Level Hackathon, PES University, Bangalore \hfill May 2024
\end{itemize}
\textbf{Line Follower Competitions:}
    \begin{itemize}
        \item Built a high-speed, high-precision line follower robot through a custom PCB and a new PID control algorithm.
        \item Ranked \textbf{1st place} at BITS Pilani, \textbf{2nd place} at Anna University, and \textbf{3rd place} at Kongu Engineering College, Erode.
    \end{itemize}
    
% Clubs Section
\section*{VOLUNTEERING - Student Clubs}

\noindent
\textbf{Data Science Community} \hfill Chennai, Tamil Nadu\\
\textit{Machine Learning / Research Supervisor} \hfill September 2022 – December 2024
\begin{itemize}
    \item Gained hands-on experience in advanced AI, ML, DL, and data science through multiple cross-domain projects.
    \item Collaborated with students from diverse backgrounds to develop cutting-edge AI solutions, including a rhythm generator.
\end{itemize}

\noindent
\textbf{SRM Team Robocon} \hfill Chennai, Tamil Nadu\\
\textit{System Integration and Electronics Subsystem Engineer} \hfill September 2022 – September 2023
\begin{itemize}
    \item Accumulated over \textbf{1,000 hours} of on-site experience in electronics, control systems, and embedded coding.
    \item Designed and integrated multifunctional robots for international competitions like ABU Robocon, covering ideation, development, testing, and deployment.
\end{itemize}

\noindent
\textbf{CINTEL's Next Gen AI} \hfill Chennai, Tamil Nadu\\
\textit{Domain Head, Robotics and Generative AI} \hfill January 2023 – September 2024
\begin{itemize}
    \item Mentored and led a team of 25 students to build robots integrating AI and computer vision capabilities.
    \item Organized a large multi-domain hackathon attended by over \textbf{1,000 students}.
\end{itemize}

% End document
\end{document}